Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-07-26 Report/convergence_centralized.tex
updated with perusu

\review{To ensure the uniqueness of the transmit precoders and the receive beamformers on all iterations, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} can be regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
	\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + c_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where \eqn{\mbf{z}} is vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem and \me{c_{k}^{(i)} > 0} is a positive constant to ensure strong convexity of the objective with some parameter \eqn{m \triangleq \min_{k} \{c_{k}^{(i)}\}} and \eqn{m > 0} as discussed in \cite{scutari-1}. Now by using the strong convexity of the modified objective in \eqref{mod_obj}, we can guarantee the uniqueness of the minimizer in each \ac{SCA} step \eqn{k} \cite{yang_yang,scutari-1}. Note that the quadratic term in \eqref{mod_obj} includes the previous solution \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} in the objective of \eqref{con-m}, which is solved in the \eqn{\ith{k}} \ac{SCA} iteration.}

>>>>

\review{To ensure the uniqueness of the transmit precoders and the receive beamformers on all iterations, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} can be regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
	\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + c_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where \eqn{\mbf{z}} is vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem and \me{c_{k}^{(i)} > 0} is a positive constant to ensure strong convexity of \eqn{f} in each step as discussed in \cite{scutari-1}. Let \eqn{m > 0} be the constant of strong convexity of \eqn{f}, where \eqn{m \triangleq \min_{k} \{c_{k}^{(i)}\}}. Using the strong convexity of the modified objective in \eqref{mod_obj}, we can guarantee the uniqueness of the minimizer in each \ac{SCA} step \eqn{k} \cite{yang_yang,scutari-1}. Note that the quadratic term in \eqref{mod_obj} includes the previous solution \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} in the objective of \eqref{con-m}, which is solved in the \eqn{\ith{k}} \ac{SCA} iteration.}
